Towards End-user Web Scraping For Customization

### 2021-03-14 paper.tex
Add Wildcard citation from Onward!

In our prior work, we presented Wildcard \citep{litt2020a}, a
customization system which enables end-users to customize websites
through direct manipulation. It does this by augmenting websites with a
table view that shows their underlying structured data. The table is
bidirectionally synchronized with the original website, so end-users can
easily customize the website by interacting with the table, including
sorting and filtering data, adding annotations, and running computations
in a spreadsheet formula language. Wildcard enables end-users to be
\emph{creators} of browser userscripts (and not just consumers) without
having to write Javascript code.

@@

In order to generate reusable scrapers from user demonstrations, our
system solves the \emph{wrapper induction} \citep{kushmerick2000} task:
generalizing from a small set of user-provided examples to a scraping
specification that will work on other parts of the website, and on
future versions of the website.

>>>>

In our prior work, we presented Wildcard \citep{litt2020a, litt2020b}, a
customization system which enables end-users to customize websites
through direct manipulation. It does this by augmenting websites with a
table view that shows their underlying structured data. The table is
bidirectionally synchronized with the original website, so end-users can
easily customize the website by interacting with the table, including
sorting and filtering data, adding annotations, and running computations
in a spreadsheet formula language. Wildcard enables end-users to be
\emph{creators} of browser userscripts (and not just consumers) without
having to write Javascript code.

@@

In order to generate reusable scrapers from user demonstrations, our
system solves the wrapper induction \citep{kushmerick2000} task:
generalizing from a small set of user-provided examples to a scraping
specification that will work on other parts of the website, and on
future versions of the website.
